---
title: "IFC_vignette"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

IFC is an R-package for data analysis of image flow cytometry.
Installation:
```{r setup}
devtools::install_github(repo = "gitdemont/IFC", ref = "master", dependencies = FALSE, local = FALSE)
```



Activation
```{r}
library(IFC)
```
For the following example, three files are needed:
- `example.rif`: raw image file
- `example.cif`: compensated image file
- `example.daf`: data analysis file

```{r}
fileNamedaf <- "example.daf"
fileNameRif <- "example.rif"
fileNameCif <- "example.cif"
```


R object can be construted from these files:

```{r}
rifn1 <- ExtractFromXIF(fileNameRif, extract_features = T, extract_images = F, extract_offsets = F, extract_stats = F, display_progress = F)
cifn1 = ExtractFromXIF(fileNameCif, extract_features = T, extract_images = T, extract_offsets = T, extract_stats = T, fast = T)
dafn1 <- ExtractFromDAF(fileNameDaf, extract_features = T, extract_images = T, extract_offsets = T, extract_stats = F, display_progress = T)
```
The obtained R object is an "IFC_data" class, whose description is given in the help (`? ExtractFromXIF` or `? ExtractFromDAF`).
GSremarque: dans le help de ExtractFromXIF, fast and recursive are difficult to understand.
GSremarque: dans le hehlp de ExtratFromXIF and ExtractFromDAF, offsets is not easy to understand.
GSremarque: dans le help de ExtractFromDAF, endianess is not clear, I am not sure everyuser know what endianess is.


For .daf file, the function readIFC can also be used:
```{r}
dafn2 = readIFC(fileNameDaf, extract_features = T, extract_images = T, extract_offsets = T, extract_stats = T)
```
GSremarque: quelle est la différence entre readIFC et ExtractfromDAF ?

Offsets (GSremarque: need to explain what is offset? also in helps?) are in object obtained from a .daf file:
```{r}
offsets_daf = dafn1$offsets
str(offsets_daf)
```

Offsets can also be extracted from .cif file:
```{r}
offsets_cif = getOffsets(fileNameCif, fast = T, display_progress = T)
```

GSremark: I am not sure that getIFD should be represented in the vignette. Anyway, for me it is difficult to understand.
- The name 'getIFD' itself seems strange as "directory" seems related to a folder
- As I undesrand, the inforamtions are related to TIFF format. If it is the case, it should mention at first in the help.
- although I don't know wat "offset", it seems strange to have the possiblity of "first" or "all".
- I don't understand what are trunc_bytes and force_trunc.
- The part "Details" of the help is hard to understand, as the "Value" is easier.
Similar remarks about getFullTag. For me, it is diffcult to understant what are these "Tags".

It is possible to produce a report (pdf file or csv file):
```{r}
ExportToReport(dafn1, write_to = c("test.pdf"), selection = 12,  precision = "light", overwrite = T, onepage = T)
```
GSrmarks on "ExportToReport": choice of name "write_to" is strange. Why not simply "Outfile"? In the example of the help, I think it is not a good idea to put the file in tmpdir. I would prefer to put it in the working directory. 


The images can be displayed and/or exported.
```{r}
disp = getInfo(fileName1, from = "analysis")
DisplayGallery(display = disp, offsets = dafn1$offsets, objects = which(dafn1$pops[["tagged_S"]]$obj)-1, extract_max = 10, forceRange = F, force_width = T, display_progress = F, base64_id = T, objects_type = "msk")
imageExport = ExportToGallery(disp, offsets = dafn1$offsets, objects = (which(dafn1$pops[["tagged_S"]]$obj)-1)[1], export = "base64",overwrite = T, dpi = 300, force_width = F, add_channels = F, scale = list(size = 8), mode = "rgb")
```
GSRemarks: name of argument "object" for DisplayGallery and ExportToGallery  (and also ExtractImages_toBase64) is strange, which simple "indices" or "objectIndices".

It is possible to extract population inidces from an object:
```{r}
popIndicesTCli <- popsGetIndices(dafn1, "tagged_cli")
```

Finally, it is possible to export data to .daf of .xif (GSRemark: can you explain what does exaclyt the code below, in term of pop and reg?)
```{r}
pop = dafn1$pops[sapply(dafn1$pops, FUN=function(x) x$type=="G")][[3]]
pop_copy = pop
pop_copy$name = paste0(pop_copy$name,"_copy")
reg = dafn1$regions[[pop_copy$region]]
reg_copy = reg
reg_copy$label = paste0(reg_copy$label,"_copy")
pop_copy$region = reg_copy$label
ExportToDAF(dafn1$fileName, write_to = "ExportFile.daf",pops = list(pop_copy),regions = list(reg_copy), verbose = T, overwrite = T)
ExportToXIF(fileName = "example.cif", write_to = "ExportFile.cif", objects = popIndicesTCli[c(7,2,3,4)], overwrite = T, fast = F)
```
GSremarks on "ExportToDAF,ExportToXIF": choice of name "write_to" is strange. Why not simply "Outfile"? In the example, I think it is not a good idea to put the file in tmpdir. I would prefer to put it in the working directory. 

GSRemarks on "ExportToXIF: name of argument "object" for DisplayGallery and ExportToGallery  (and also ExtractImages_toBase64 is strange, which simple "indices" or "objectIndices".


